### 2017-08-15 Tex_Dissertation/MSc_dissertation.tex
introchange

\begin{figure}[!hb]
  \centering
  \includegraphics[width=0.7\linewidth]{{images/ATLAS_SUSY_Stop_tLSP}.png}
  \label{fig2.15}
  \caption{\scriptsize{Mass exclusion limits at stop-neutralino plane.}}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.6\linewidth, scale=5]{{images/gluino}.png}
  \label{}
  \caption{\scriptsize{Mass exclusion limits at stop-gluino plane.}}
\end{figure}

>>>>

\begin{figure}[!hb]
  \centering
  \includegraphics[width=0.7\linewidth]{{images/ATLAS_SUSY_Stop_tLSP}.png}
  \label{fig2.15}
  \caption{\scriptsize{Mass exclusion limits at stop-neutralino plane (combined summary plot from ATLAS 
  twiki).}}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.6\linewidth, scale=5]{{images/gluino}.png}
  \label{}
  \caption{\scriptsize{Mass exclusion limits at stop-gluino plane~\cite{atlassearch}.}}
\end{figure}
